Refinements for open automata

### 2022-01-25 2021-Refinement/paper/refinementarticle.tex
proof in progress
proof in progess

Yet according to the relation between $A_1$ and $A_2$ we have  forall $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:

@@

\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{\begin{array}{c} p\in P\\ j \in J'_{2p}

@@

\section{Proof of Context Refinement}
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are same with renaming). We define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge s^1_3 = s^2_3\]

\TODO{Old version \[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = q_{3} \\ \bot & \text{otherwise}} \]}
We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
\begin{enumerate}
\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial states are reachable and by renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

We have by hypothesis:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{03}(v)=\sigma_{03}(v)\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v)\\
\iff & R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v) \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma_{023}}
\end{align*}
\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
where 
\begin{align*}
&V_{13}= V_1\uplus V_3 \text{ and }
V_{23}= V_2\uplus V_3\\
& H'=J_3'\uplus H \setminus \{k\} \subseteq J_3'\uplus \mpar{J_1' \cap J_2'} \setminus \{k\} = \mpar{J_3'\uplus J_1' \setminus \{k\} } \cap \mpar{J_3'\uplus J_2' \setminus \{k\}} = J_{13}'\cap J_{12}'\\
\end{align*}

@@

We have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}}  \qquad (*)
\end{multline*}	
\smallskip

The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3}{}{3}{3} $, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
% \[  \choice{
%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
%	& \text{if } k \in J'_{1} \\
%	\OTx{1}{}{1}{1}	 & \text{otherwise}
%	} \]
\[
\choice{
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
}
\]

@@

By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{itemize}
\TODO{Pas termine: valider d'abord la definition de R}
\item The last formula to prove is the following:
\begin{multline*}
\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23},\\ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_2} \vdash \left(R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
By hypothesis we have the following:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
By adding the term $\displaystyle{\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}}$ to both sides of the implication, we get: 
\begin{multline*}
\forall \mpar{s_1, s_2,s_3} \in S_1 \times S_2 \times S_3, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}\right)
\end{multline*}
By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-locking,  thus we can write the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]

>>>>

Yet according to the relation between $A_1$ and $A_2$ we have  for all $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:

@@

\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup  \bigcup_{\begin{array}{c} \subbox{p\in P}\\ \subbox{j \in J'_{2p}}

@@

\section{Proof of Context Refinement}
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. The proof requires to resort to rename the elements (states, variables, etc) of an automaton according to the one to which they belong.

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
\begin{enumerate}
\item First, we have to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement holds:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.
And secondly, because the domain of the substitution function is disjoint from the others, it has an effect only on the related elements, and relying on the  fact that initial states are reachable we  have:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge\underbrace{  \bigwedge_\subbox{v_3\in V_3} \sigma^1_{03}(v^1_3)=\sigma^2_{03}(v^2_3)\wedge s^1_3 = s^2_3}_{\Longleftrightarrow~\top}\\
\iff & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\iff & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
where 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H'=J_3'\uplus H \setminus \{k\} \subseteq J_3'\uplus \mpar{J_1' \cap J_2'} \setminus \{k\} = \mpar{J_3'\uplus J_1' \setminus \{k\} } \cap \mpar{J_3'\uplus J_2' \setminus \{k\}} = J_{13}'\cap J_{12}'\\
\end{align*}

@@

We have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}}  \qquad \quad (*)
\end{multline*}	
\smallskip
Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained either by the composition of the transition $t_1=\OTx{1}{}{1}{1}$ and the transition %$t_3^1=\OTxup{3}{1} $, if $k \in J_1'$; or by the transition $t_1$ and the state $s_3^1$, otherwise (if $k \notin J_1'$).
%%%% Attention deactiver ici
\[
\choice{
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} & \text{ if } k \in J'_{1} \\
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
}
\]

By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$. For any $t_{23x}$  there will then be two cases according on how it is built:

\[
\choice{
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3} & \text{ if } k \in J'_{2x} \\
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
}
\]

So have to prove the following:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  = 
	\mpar{ J'_{2x}\uplus J^{2 \prime}_{3}  \setminus \mbrc{k}} \cap  \mpar{J^{2 \prime}_{3} \uplus H \setminus \mbrc{k}} \\
		& = J^{2 \prime}_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
		& = J^{1 \prime}_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J^{1 \prime}_{3} \uplus H \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J^{2 \prime}_3 \uplus H \setminus \mbrc{k}} \\
\end{align*}

For the rest of the formula we will also consider the two cases separately.

\begin{itemize}
\item If $k \in J'_1$: we will extend the valuation context of the variables to cover the variables of the transition $t_3$. Based on this fact we have: $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ because composition doesn't change the resulting actions, nor their variables. 
We also have 
${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj}}$ since the actions of the holes in $J_3$ coincide on both sides. And the following statements: 
$g_{13} \Leftrightarrow g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k}$, 
$g_{23x}  \Leftrightarrow g_{2x} \wedge g_3 \wedge \alpha_3=\beta_{2xk}$ and $\beta_{1k} = \beta_{2xk}$\\

From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:\\

$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{13}}  \cup\!\!\! \bigcup_{j \in J'_{23x}} \!\!\!\fvars{\beta_{13j} } } \setminus  \mpar{V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}}},$
\begin{multline*}
R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{2xk} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
			 g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
		\end{array}}   
\end{multline*}

By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{itemize}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%555

 that gives,  according to Definition \ref{Def:CompOA}

The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3^1}{}{3}{3}$, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
% \[  \choice{
%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
%	& \text{if } k \in J'_{1} \\
%	\OTx{1}{}{1}{1}	 & \text{otherwise}
%	} \]
\[
\choice{
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
}
\]

@@

By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{itemize}
\TODO{Pas termine: valider d'abord la definition de R}
\item The last formula to prove is the following:
\begin{multline*}
\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23},\\ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_2} \vdash \left(R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
By hypothesis we have the following:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
By adding the term $\displaystyle{\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}}$ to both sides of the implication, we get: 
\begin{multline*}
\forall \mpar{s_1, s_2,s_3} \in S_1 \times S_2 \times S_3, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}\right)
\end{multline*}
By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-locking,  thus we can write the following:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
\end{enumerate}
